{{< var titll >}}

### 2024-07-19 presentation.qmd
break

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::appsn)
rsr  <- selreport(ManifoldDestiny::apprn)
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`
\end{equation*}

Election outome 
  - Integral `r round(polynom::integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)`
  - Counting `r round(ssr[[1]]$desms[7,2],3)`

```{r}
knitr::knit_exit()
```

@@

\begin{equation*}
$f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`$
\end{equation*}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(polynom)
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
ssr <- selreport(ManifoldDestiny::appsn)
rsr  <- selreport(ManifoldDestiny::apprn)
round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))`
\end{equation*}

Election outome:

- Integral `r round(polynom::integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)`
- Counting `r round(ssr[[1]]$desms[7,2],3)`

@@

\begin{equation*}
f(x)_{0}^{1}=`r round(integral(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients))))`
\end{equation*}
